Liptschiz

### 2024-02-23 lipschitz/valabstraction.tex
update constraints

The following two plots show its shape:

>>>>

A more direct way to establish the constraints is as follows: \begin{align*}
	& y+x'_i \leq a\beta_i \quad\wedge \quad y+x'_i\geq (1-a)\alpha_i\\	
	& x_i' \leq a'\beta_i \quad\wedge \quad x_i'\geq (1-a')\alpha_i\\
	&\hat{y}_i \leq -a\gamma_i \quad\wedge \quad	\hat{y}_i \geq a'\gamma_i \\
	&	\hat{y}_i \leq y_i+(1-a)\gamma_i \quad\wedge \quad	\hat{y}_i \geq y_i - (1-a')\gamma_i \\
	&	\hat{y}_i \leq -x'_i+(1-a)\beta_i \quad\wedge \quad	\hat{y}_i \geq -x'_i+(1-a')\alpha_i \\
	&	\hat{y}_i \leq y_i+x'_i+(1-a)(-\alpha_i)\quad\wedge \quad	\hat{y}_i \geq y_i+x'_i+(1-a')(-\beta_i) \\
\end{align*}The following two plots show its shape:
